### 2022-06-09 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@ae2c54fa2068f9f57b1e56217327ebc87637c577 🚀

\begin{figure}
\hypertarget{fig:bias}{%
\centering
\includegraphics{figures/changing-bias.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on \(F_1\), informedness, MCC,
and \(\kappa\). Accuracy increases with skill, but also increases when
the bias tends towards estimating \emph{fewer} interactions. The \(F_1\)
score increases with skill but also increases when the bias tends
towards estimating \emph{more} interactions. Interestingly, \(\kappa\)
responds as expected to skill (being negative whenever \(s < 0.5\)), and
peaks for values of \(b \approx 0.5\); nevertheless, the value of bias
for which \(\kappa\) is maximized in \emph{not} \(b=0.5\), but instead
increases with classifier skill. In other words, at equal skill,
maximizing \(\kappa\) would lead to select a \emph{more} biased
classifier.}\label{fig:bias}
}
\end{figure}

@@

In order to pick the best adjacency matrix for a given trained machine,
we performed a thresholding approach using 500 steps on predictions from
the testing set, and picking the threshold that maximized Youden's
informedness. During the thresholding step, we measured the area under
the receiver operating characteristic (ROC-AUC) and precision-recall
(PR-AUC) curves, as measures of overall performance over the range of
returned values. We report the ROC-AUC and PR-AUC, as well as a suite of
other measures as introduced in the next section, for the best
threshold. The ensemble model was generated by summing the predictions
of all component models on the testing set (ranged in \([0,1]\)), then
put through the same thresholding process. The complete code to run the
simulations is available at \texttt{10.17605/OSF.IO/JKEWD}.

>>>>

\begin{figure}
\hypertarget{fig:bias}{%
\centering
\includegraphics{figures/changing-bias.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on \(F_1\), informedness, MCC,
and \(\kappa\). Accuracy increases with skill, but also increases when
the bias tends towards estimating \emph{fewer} interactions (this
follows from the derivations in the text, not shown in the figure).
Interestingly, \(\kappa\) responds as expected to skill (being negative
whenever \(s < 0.5\)), and peaks for values of \(b \approx 0.5\);
nevertheless, the value of bias for which \(\kappa\) is maximized in
\emph{not} \(b=0.5\), but instead increases with classifier skill. In
other words, at equal skill, maximizing \(\kappa\) would lead to select
a \emph{more} biased classifier.}\label{fig:bias}
}
\end{figure}

@@

In order to pick the best confusion matrix for a given trained machine,
we performed a thresholding approach using 500 steps on predictions from
the testing set, and picking the threshold that maximized Youden's
informedness. During the thresholding step, we measured the area under
the receiver operating characteristic (ROC-AUC) and precision-recall
(PR-AUC) curves, as measures of overall performance over the range of
returned values. We report the ROC-AUC and PR-AUC, as well as a suite of
other measures as introduced in the next section, for the best
threshold. The ensemble model was generated by summing the predictions
of all component models on the testing set (ranged in \([0,1]\)), then
put through the same thresholding process. The complete code to run the
simulations is available at \texttt{10.17605/OSF.IO/JKEWD}.
